### 2018-12-06 manuscript/manuscript.rmd
parsing basic info from iqtree runs

```{r preliminaries}
library( tidyverse )
library( magrittr )
library(viridis)

@@

papers = read_tsv( "../data_processed/tables/previously_published_manuscripts.tsv" )
datasets = read_tsv( "../data_processed/tables/previously_published_datasets.tsv" )
analyses = 
	read_tsv( "../data_processed/tables/previously_published_analyses.tsv", col_types = 'iccccccccccclnnnncc' ) %>%
	mutate( clade = factor( clade, levels= c( 'Choanimalia', 'Holozoa', 'Opisthokonta' ) ) )

@@

>>>>

```{r preliminaries}
library( tidyverse )
library( magrittr )
library(viridis)
library(ape)

@@

papers = read_tsv( "../data_processed/tables/previously_published_manuscripts.tsv" )
datasets = read_tsv( "../data_processed/tables/previously_published_matrices.tsv" )
analyses = 
	read_tsv( "../data_processed/tables/previously_published_analyses.tsv", col_types = 'iccccccccccclnnnncc' ) %>%
	mutate( clade = factor( clade, levels= c( 'Choanimalia', 'Holozoa', 'Opisthokonta' ) ) )

@@

trees_path = "../trees_new/"
tree_file_names = list.files(path = trees_path, pattern = ".+\\.contree$")

trees = lapply(
	tree_file_names,
	function( tree_file ){
		print(tree_file)
		log_file = sub( "contree$", "log", tree_file )

		tree_file_path = paste(c(trees_path, tree_file), collapse="")
		log_file_path = paste(c(trees_path, log_file), collapse="")

		base_name = sub( "\\.contree$", "", tree_file )
		elements = strsplit(base_name, "\\.") %>% unlist()
		matrix_name = elements[1]
		model_name = elements[2]

		tree = read.tree( file = tree_file_path )

		# Get the clades of the tips
		clades = 
			taxonomy_reference$clade_assignment[ 
				match( tree$tip.label, taxonomy_reference$relabelled_name ) 
				]

		# Get the outgroup sampling

		outgroup = NA

		sampling = "Metazoa"
		if( "Choanoflagellida" %in% clades ){
			sampling = "Choanimalia"
			outgroup = which( clades == "Choanoflagellida" )
		}

		if( ("Ichthyosporea" %in% clades) | ("Filasterea" %in% clades) ){
			sampling = "Holozoa"
			outgroup = c( which( clades == "Ichthyosporea" ),  which( clades == "Filasterea" ))
		}

		if( "Fungi" %in% clades ){
			sampling = "Opisthokonta"
			outgroup = which( clades == "Fungi" )
		}

		# Reroot the tree
		# Use a single taxon from the outgroup since the outgroup is not guaranteed to be monophyletic
		tree = root( tree, outgroup[1] )

		# Get the clades of the tips again, since tip order has changed
		clades = 
			taxonomy_reference$clade_assignment[ 
				match( tree$tip.label, taxonomy_reference$relabelled_name ) 
				]

		# Stuff a few other things into the tree object
		tree$matrix = matrix_name
		tree$model = model_name
		tree$modelfinder = FALSE
		tree$clades = clades
		tree$sampling = sampling

		# parse model
		log_lines = read_lines( log_file_path )

		best_line = log_lines[ grepl("Best-fit model:", log_lines) ]

		if( length(best_line) > 1 ){
			warning("More than one best model found")
		}

		if( length(best_line) > 0 ){
			tree$modelfinder = TRUE
			elements = strsplit( best_line[1], " " ) %>% unlist()
			tree$model = elements[3]
		}

		return( tree )
	}
)

tree_summary = lapply(
	trees,
	function( tree ){
		data.frame(
			matrix = tree$matrix,
			model = tree$model,
			modelfinder = tree$modelfinder,
			sampling = tree$sampling,
			stringsAsFactors = FALSE
		)
	}
) %>% bind_rows()
